---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `uwquantreg`: unit-Weibull quantile regression

<!-- badges: start -->
<!-- badges: end -->

The goal of `uwquantreg` is to provide tools for fitting unit-Weibull quantile regression 
proposed by [Mazucheli et al. (2020)](https://www.tandfonline.com/doi/abs/10.1080/02664763.2019.1657813?journalCode=cjas20).
Also, the Zero-or-One inflation model are also available.

## Installation

You can install the development version of `uwquantreg` from [GitHub](https://github.com/AndrMenezes/uwquantreg) with:

``` r
# install.packages("devtools")
devtools::install_github("AndrMenezes/uwquantreg")
```
## Example

The packages follows the structure of `glm` objects. The main functions are `uwquantreg` and `zouwquantreg`.

```{r example, warning=FALSE}
library(uwquantreg)

fit <- uwquantreg(phpws ~ mhdi + incpc + region + log(pop), 
                  data = water, 
                  tau = 0.5, 
                  link = "logit")
fit
summary(fit)
confint(fit)
```

The currently methods implemented are
```{r methods}
methods(class = "uwquantreg")
```


